The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-10-12 paper/paper.tex
denonymize

\author{
    Person One
   \\
     \\
   \\
  \texttt{\href{mailto:personone@domain.com}{\nolinkurl{personone@domain.com}}} \\
   \And
    Person Two
   \\
     \\
   \\
  \texttt{\href{mailto:persontwo@domain.com}{\nolinkurl{persontwo@domain.com}}} \\
  }

@@

  CoD is fairly unique compared to other esports in that it runs on an
  annual lifecycle, with releases coming in the late fall. A new game
  under the same brand---``Call of Duty''---is published every year by a
  rotating set of developers. Each new game bears resemblance to past
  ones, often introducing relatively small variations (``improvements'')
  to graphics, game modes, and other facets of gameplay. During the CDL
  era, the games released have been ``Modern Warfare'' (2020 season),
  ``Cold War'' (2021 season) and ``Vanguard'' (2022 season).}, totaling
7,792 rounds across 852 series.\footnote{288 of the series occur in
  major tournaments, which are considered to be more competitive than
  the qualifiers since they are played in person (COVID-permitting),
  eliminating randomness due to online latency and ping. The qualifiers
  are played online.} Data has been collected in spreadsheets by
community member ``IOUTurtle''.\footnote{Raw data:
  \url{https://linktr.ee/CDLArchive}. Cleaned data:
  \url{https://github.com/author/repo/blob/master/data/file.csv}.}

>>>>

\author{
    Tony ElHabr
   \\
     \\
   \\
  \texttt{\href{mailto:anthonyelhabr@gmail.com}{\nolinkurl{anthonyelhabr@gmail.com}}} \\
   \And
    Andrew ElHabr
   \\
    School of Industrial and Systems Engineering (ISyE) \\
    Georgia Institute of Technology \\
  Atlanta, Georgia, USA \\
  \texttt{\href{mailto:andrewelhabr@gatech.edu}{\nolinkurl{andrewelhabr@gatech.edu}}} \\
  }

@@

  CoD is fairly unique compared to other esports in that it runs on an
  annual lifecycle, with releases coming in the late fall. A new game
  under the same brand---``Call of Duty''---is published every year by a
  rotating set of developers. Each new game bears resemblance to past
  ones, often introducing relatively small variations (``improvements'')
  to graphics, game modes, and other facets of gameplay. During the CDL
  era, the games released have been ``Modern Warfare'' (2020 season),
  ``Cold War'' (2021 season) and ``Vanguard'' (2022 season).}, totaling
7,792 rounds across 852 series.\footnote{288 of the series occur in
  major tournaments, which are considered to be more competitive than
  the qualifiers since they are played in person (COVID-permitting),
  eliminating randomness due to online latency and ping. The qualifiers
  are played online.} Data has been collected in spreadsheets by
community member ``IOUTurtle''.\footnote{Raw data:
  \url{https://linktr.ee/CDLArchive}. Cleaned data:
  \url{https://github.com/tonyelhabr/cod_snd/blob/master/data/cod_rounds.csv}.}
